\documentclass{article}
\usepackage{lm-latex}

\title{Installation}

\begin{document}

\maketitle

\tableofcontents

\input{project_abstract}

\section{Software Requirements}

Lifecycle Manager is built as a \href{http://trac.edgewall.org/}{Trac} plugin
and requires no modification to Trac's codebase or an existing Trac installation.
The plugin has been tested only with the latest stable version of Trac: 
\href{http://trac.edgewall.org/wiki/TracDownload}{Trac 10.x}.

In this respect, the other software requirements for using Lifecycle Manager are
only those of Trac. See Trac's
\href{http://trac.edgewall.org/wiki/TracInstall}{Installation Guide} for further
information.

\subsection{Python Version}
\label{sec:python-version}

Of particular interest, however, is your version of Python. Lifecycle Manager is
built to a particular version of Python. Please check your Python documentation
for your current version.


\section{Installation Procedure}

Download Lifecycle Manager from this location: XXX. Be sure to choose the
version matching your Python installation (see section \ref{sec:python-version} above).

The distribution of Lifecycle Manager is a `tarball', or tape-archive file
compressed with GNU's gzip. Download the tarball and extract as follows (where
\texttt{\$} indicates the shell prompt):
\begin{verbatim}
$ tar xzvf TracRequirements-0.1.tar.gz
\end{verbatim}
You will see output similar to the following:
\begin{verbatim}
AUTHORS
INSTALL
NEWS
README
TODO
TracRequirements-0.1-py2.4.egg
pdf/coding_policy.pdf
pdf/database_schema.pdf
pdf/dream_design_policy.pdf
pdf/general_document_changeset_policy.pdf
pdf/metrics.pdf
pdf/proposed_ontology.pdf
pdf/reports.pdf
pdf/requirements_policy.pdf
pdf/software_requirements_specification.pdf
pdf/testing_policy.pdf
pdf/wiki_usage_policy.pdf
\end{verbatim}
The file of particular interest right now is
\texttt{TracRequirements-0.1-py2.4.egg}, which is known as the `egg'. Note that the
string \texttt{py2.4} may differ depending on your Python version (see section
\ref{sec:python-version} above). Copy the egg to your Trac installation's
\texttt{plugins} directory. For example,
\begin{verbatim}
cp TracRequirements-0.1-py2.4.egg /usr/share/trac/plugins
\end{verbatim}
Next restart your Trac webserver.

After your Trac server has restarted, the Lifecycle Manager plugin should be
loaded. Check the `About/Plugins' page in your Trac installation at this
address: \texttt{http://trac-install/about/plugins}. In the list you should be
able to find `RequirementComponent,' `NewrequirementModule,' and
`RequirementModule.'

Next you are ready to set up permissions to use Lifecycle Manager.


\section{Permissions}

Lifecycle Manager has the following permission hierarchy:
\begin{itemize}
  \item \texttt{REQUIREMENT\_APPEND} -- comment on a requirement
  \item \texttt{REQUIREMENT\_CREATE} -- create or modify a requirement
  	\begin{itemize}
      \item \texttt{REQUIREMENT\_MODIFY} -- modify the description of a
      requirement or comment on a requirement
    \end{itemize}
  \item \texttt{REQUIREMENT\_VIEW} -- view a requirement or list of requirements
  \item \texttt{REQUIREMENT\_MODIFY} -- modify the description of a requirement
  or comment on a requirement
  	\begin{itemize}
      \item \texttt{REQUIREMENT\_APPEND} -- comment on a requirement
    \end{itemize}
  \item \texttt{REQUIREMENT\_ADMIN} -- perform any action on a requirement
  	\begin{itemize}
      \item \texttt{REQUIREMENT\_CREATE} -- create or modify a requirement
      \item \texttt{REQUIREMENT\_VIEW} -- view a requirement or a list of requirements
    \end{itemize}
\end{itemize}

Your Trac users' permissions must be enabled to one or more of the above in
order to use Lifecycle Manager. For example, add the permission
\texttt{REQUIREMENT\_VIEW} to a user `joe', perform the following step:
\begin{verbatim}
trac-admin /path-to-trac-env permission add joe REQUIREMENT_VIEW
\end{verbatim}

\section{Conclusion}

After the egg has been installed and permissions delegated, Lifecycle Manager is
ready to use. Users who can view the list of requirements (permission
\texttt{REQUIREMENT\_VIEW}) will see a button in their Trac toolbar called
`Requirements.' Click this button to begin!

\end{document}
